Scalable Clustering of Genotype Information using MapReduce

### 2015-04-08 doc/publications/journal2014/paper.tex
fix bio

\section{Author CV}
\paragraph{Aidan R O'Brien, BSc(Hons), is a joined researcher at Newcastle University and CSIRO and interested in BigData approaches for pan-cancer research.}

>>>>

\section{Author CV}
\paragraph{Aidan R O'Brien, BBiot(Hons), is a joined researcher at Newcastle University and CSIRO and interested in BigData approaches for pan-cancer research.}
